Results

### 2024-05-01 Analysis/04_Summarise_results.Rmd
Update 04_Summarise_results.Rmd

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
#rm1 = "extant", rm2 = "historic", rm3 = "prehistoric"
extants <- grep("rm1", colnames(empirical_results$empirical$results_table))
historics <- grep("rm2", colnames(empirical_results$empirical$results_table))
prehistorics <- grep("rm3", colnames(empirical_results$empirical$results_table))
## Reorder by percentage removed (historics > prehistorics > extants)
empirical_results$empirical$results_table <- empirical_results$empirical$results_table[, c(historics, prehistorics, extants)]
```

@@

## Fancier names
fancy_names <- c("TPD[TPD]\nregularity",
                 "hypervolume[BAT]\nregularity",
                 "dendrogram[BAT]\nregularity",
                 "dissimilarity[FD]\nregularity",
                 "TPD[TPD]\ndivergence",
                 "hypervolume[BAT]\ndivergence",
                 "dendrogram[BAT]\ndivergence",
                 "dissimilarity[melodicMPD]\ndivergence(MPD)",
                 "dissimilarity[melodicRao]\ndivergence(Rao)",
                 "dissimilarity[FD]\ndivergence(Rao)",
                 #"dissimilarity[FD]\ndivergence",
                 "TPD[TPD]\nrichness",
                 "hypervolume[BAT]\nrichness",
                 "convex hull[BAT]\nrichness",
                 "dendrogram[BAT]\nrichness")
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 7), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))

@@

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 4.5)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = rev(fancy_names), pch = c(19,15,17))
dev.off()
```

@@

## Medians
points(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
points(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
points(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
points(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
points(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## Linkings
lines(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
lines(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
lines(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
lines(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
lines(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## 95% CI
dimensions <- c(2,3,4,5,8)
for(one_ci in 1:5) {
  lines(y = c(times_tree[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.00, col = metric_cols[1])
}
for(one_ci in 1:5) {
  lines(y = c(times_dissimilarity[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.04, col = metric_cols[2])
}
for(one_ci in 1:5) {
  lines(y = c(times_hull[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.08, col = metric_cols[3])
}
for(one_ci in 1:5) {
  lines(y = c(times_hypervolume[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.12, col = metric_cols[4])
}
for(one_ci in 1:5) {
  lines(y = c(times_probabilities[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.16, col = metric_cols[5])
}
## legend
legend("topleft", col = metric_cols, pch = 19, legend = c("tree", "dissimilarity", "convex hull", "hypervolume", "probability density"))

>>>>

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
#rm1 = "extant", rm2 = "historic", rm3 = "prehistoric"
extants <- grep("rm1", colnames(empirical_results$empirical$results_table))
historics <- grep("rm2", colnames(empirical_results$empirical$results_table))
# prehistorics <- grep("rm3", colnames(empirical_results$empirical$results_table))
## Reorder by percentage removed (historics > prehistorics > extants)
empirical_results$empirical$results_table <- empirical_results$empirical$results_table[, c(historics, extants)]
```

@@

## Fancier names
fancy_names <- rev(
               c("Functional evenness\nprobability density\nTPD::REND",
                 "Functional evenness\nhypervolume\nBAT::kernel.evenness",
                 "Functional evenness\ndendrogram\nBAT::evenness",
                 "Functional evenness\ndistances\nFD::dbFD()$FEve",
                 "Divergence\nprobability density\nTPD::REND",             
                 "Functional dispersion\nhypervolume\nBAT::kernel.dispersion",
                 "Functional dispersion\ndendrogram\nBAT::dispersion",
                 "Melodic Mean Pairwise Distance\ndistances\nmelodic.rao",
                 "Melodic Rao\ndistances\nmelodic.rao",
                 "Rao's quadratic entropy\ndistances\nFD::dbFD()$RaoQ",
                 #"dissimilarity[FD]\ndivergence",
                 "Functional richness\nprobability density\nTPD::REND",
                 "Functional richness\nhypervolume\nBAT::kernel.alpha",
                 "Functional richness\nconvex hull\nBAT::hull.alpha",
                 "Alpha diversity\ndendrogram\nBAT::alpha"))
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 6), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))

@@

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 11, width = 4.5)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = fancy_names, pch = c(19,15,17))
dev.off()
```

@@

## Medians
points(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
points(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
points(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
points(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
points(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## Linkings
lines(x = c(2,3,4,5,8)+0.00, c(times_tree[2,]), pch = 19, col = metric_cols[1])
lines(x = c(2,3,4,5,8)+0.04, c(times_dissimilarity[2,]), pch = 19, col = metric_cols[2])
lines(x = c(2,3,4,5,8)+0.08, c(times_hull[2,]), pch = 19, col = metric_cols[3])
lines(x = c(2,3,4,5,8)+0.12, c(times_hypervolume[2,]), pch = 19, col = metric_cols[4])
lines(x = c(2,3,4,5,8)+0.16, c(times_probabilities[2,]), pch = 19, col = metric_cols[5])
## 95% CI
dimensions <- c(2,3,4,5,8)
for(one_ci in 1:5) {
  lines(y = c(times_tree[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.00, col = metric_cols[1])
}
for(one_ci in 1:5) {
  lines(y = c(times_dissimilarity[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.04, col = metric_cols[2])
}
for(one_ci in 1:5) {
  lines(y = c(times_hull[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.08, col = metric_cols[3])
}
for(one_ci in 1:5) {
  lines(y = c(times_hypervolume[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.12, col = metric_cols[4])
}
for(one_ci in 1:5) {
  lines(y = c(times_probabilities[c(1,3), one_ci]), x = rep(dimensions[one_ci], 2)+0.16, col = metric_cols[5])
}
## legend
legend("topleft", col = metric_cols, pch = 19, legend = c("dendrogram", "dissimilarity", "convex hull", "hypervolume", "probability density"))
